### 2020-03-03 doc/icfp20/music.tex
add piston example to Main.agda; explain chords

@@

>>>>

[TODO] Maybe need to explain degrees, instead of duration and notes.

@@

\paragraph{Chords}

A \emph{chord} refers to a set of simultaneously sounding pitches.
The most common pattern of chords is called \emph{triads},
consisting of three notes separated by (major or minor) 3rd intervals.
Chords are usually denoted by roman numerals representing the
lowest note (the \emph{root}).
We define triads as a datatype \texttt{Triad} with constructors
\texttt{I}, \texttt{II}, etc., and obtain their constituent notes
(packaged into a three-element vector) via a function
\texttt{triadDegrees}.
